Supporting Information

### 2017-05-29 portfolio/text/supp.Rnw
Tweak format for editorial office

\documentclass[12pt]{article}
\usepackage{geometry}
\geometry{verbose, letterpaper, tmargin = 2.54cm, bmargin = 2.54cm,
  lmargin = 2.54cm, rmargin = 2.54cm}
\geometry{letterpaper}
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{setspace}
\usepackage{booktabs}
\usepackage{verbatim}
\usepackage{amsmath}
\usepackage{url}
\usepackage{mathtools}
\usepackage{lineno}
\usepackage{xcolor}
\renewcommand\linenumberfont{\normalfont\tiny\sffamily\color{gray}}
\modulolinenumbers[2]

% Linux Libertine:
\usepackage{textcomp}
\usepackage[sb]{libertine}
\usepackage[varqu,varl]{inconsolata}% sans serif typewriter
\usepackage[libertine,bigdelims,vvarbb]{newtxmath} % bb from STIX
\usepackage[cal=boondoxo]{mathalfa} % mathcal
%\useosf % osf for text, not math
\usepackage[supstfm=libertinesups,%
  supscaled=1.2,%
  raised=-.13em]{superiors}

@@

% Fix line numbering and align environment
% http://phaseportrait.blogspot.ca/2007/08/lineno-and-amsmath-compatibility.html
\newcommand*\patchAmsMathEnvironmentForLineno[1]{%
  \expandafter\let\csname old#1\expandafter\endcsname\csname #1\endcsname
  \expandafter\let\csname oldend#1\expandafter\endcsname\csname end#1\endcsname
  \renewenvironment{#1}%
     {\linenomath\csname old#1\endcsname}%
     {\csname oldend#1\endcsname\endlinenomath}}%
\newcommand*\patchBothAmsMathEnvironmentsForLineno[1]{%
  \patchAmsMathEnvironmentForLineno{#1}%
  \patchAmsMathEnvironmentForLineno{#1*}}%
\AtBeginDocument{%
\patchBothAmsMathEnvironmentsForLineno{equation}%
\patchBothAmsMathEnvironmentsForLineno{align}%
\patchBothAmsMathEnvironmentsForLineno{flalign}%
\patchBothAmsMathEnvironmentsForLineno{alignat}%
\patchBothAmsMathEnvironmentsForLineno{gather}%
\patchBothAmsMathEnvironmentsForLineno{multline}%
}

@@

We checked our models with a two-stage modelling approach
using the R package lme4 \citep{bates2015}.
To do this, we fit the initial model of the mean component $\log(R_{i,t})$
and then fit the second model to the log absolute value of the
residuals, $\log | \widehat{\log(R_{i,t})} - \log(R_{i,t}) |$.
Most importantly, (1) this model does not carry uncertainty
from the first mean-component model to the variance-component model, but
(2) it also leaves the residuals in the mean-component model strongly
heteroskedastic and therefore improperly weights individual data points, and
(3) does not allow for proper modelling of the strategy-level predictors,
$\eta_1$ and $\eta_2$. Nonetheless, it provides a check that our results
from the Stan model are approximately correct and allowed us
to quickly iterate and build intuition about the models.
A version of the Stan model without the variance-component
matched the estimates of the same model in lme4 almost exactly.

@@

\bibliographystyle{apalike}
\bibliography{refs}

@@

\begin{table}[h!]
\scriptsize
  \centering
  \caption{Labels and descriptions of unique fishing strategies. In many cases,
a particular strategy represents a group of similar permits across areas
or vessel sizes. The column ``Main species'' indicates species that make up at
least 10\% of the total revenue across all years and individuals for that
fishing strategy. ``Sock'' refers to sockeye salmon.}
  \label{tab:strategies}
  \begin{tabular}{llll}
  \toprule
\input{../figs/strategy-table.tex}
  \end{tabular}
\end{table}

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=1\textwidth]{../figs/stan-gg-spoke-all.pdf}
\caption{The effect of adding a permit to one's strategy
on estimated revenue variability and median revenue.
This is an extended version of Fig.~2 that includes all major
strategy combinations.}
\label{fig:spoke-all}
\end{center}
\end{figure}

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=5in]{../figs/stan-main-effects.pdf}
\caption{Main effects from the hierarchical model
predicting revenue ($\beta$) and variability ($\gamma$) in revenue.
The $\eta$ coefficients represent strategy-level predictors
relating mean species diversity and mean days fished
within a strategy
(both centered by their means and divided by
two times their standard deivations)
to the magnitude of residual error.}
\label{fig:fe}
\end{center}
\end{figure}

@@

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=1.06\textwidth]{../figs/stan-str-posteriors-dot.pdf}
\caption{Estimates of within-strategy effects from the hierarchical model.
Panels refer to parameters in equations \ref{eq:mean} and \ref{eq:cv}.
Shown are medians (dots) and 50\% and 95\% credible intervals
(thick and thin line segments).
Strategies are ordered from high to low mean
species diversity from top to bottom.}
\label{fig:re}
\end{center}
\end{figure}

@@

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=1.05\textwidth]{../figs/stan-offset-break-anti-spaghetti.pdf}
\caption{Effects of (A) generalizing and (B) specializing from year-to-year for
  individual permit holders \emph{within} the \Sexpr{nstr} most common
  strategies. Changing species diversity from year-to-year is associated with
  higher variability for individuals within the strategies above the zero line.
  Generalizing (A) or specializing (B) is associated with greater expected
  revenue ratios to the right of the zero line and lower expected revenue ratios
  to the left of the zero line. These effects are estimated holding fishing
  season length constant from year-to-year. Dots and line segments represent
  medians and 50\% credible intervals of posteriors. Panel B and Fig.~4 are the
  same.}
\label{fig:mirror}
\end{center}
\end{figure}

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=0.6\textwidth]{../figs/stan-offset-break-anti-spaghetti-specializing-no-effort.pdf}
\caption{Same as Fig.~4 but without the effort (days fished) predictor and
  without its interaction with species diversity.}
\label{fig:noeffort}
\end{center}
\end{figure}

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=1\textwidth]{../figs/itq-combined.pdf}
\caption{The effect of IFQs (individual fishing quotas) on model estimates. (A)
  Posterior density of the ratio between strategy-level estimates of
  standardized revenue variability ($\gamma_{0j}$'s) after the introduction of
  IFQs vs.\ before the introduction of IFQs. (B) Estimates (medians) of the
  effect of generalizing (increasing species diversity) on variability
  ($\gamma_{1j}$'s) for the full model (``Grouped'') compared to a model where
  separate effects are estimated before and after IFQs were introduced (``IFQ
  split''). Pattern looks similar for the effect of specializing on variability
  ($\gamma_{2j}$'s) and is not shown.}
\label{fig:ifq}
\end{center}
\end{figure}

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=1\textwidth]{../figs/strategy-year-effects.pdf}
\caption{Strategy-year intercept estimates ($\beta_{0,j,t}$ in
Eq.~\ref{eq:mean}) from the hierarchical model.
Shown are 40 samples from the posterior distribution.}
\label{fig:str-yrs}
\end{center}
\end{figure}

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=1\textwidth]{../figs/stan-offset-panel-mean-resid.png}
\caption{The log-absolute value residuals from the mean-component model (Eq.~\ref{eq:mean}).
These residuals are modelled in the variance-component model
(Eq.~\ref{eq:cv}).
Breakpoint linear regression fits are overlaid in red for visual interpretation.}
\label{fig:resid}
\end{center}
\end{figure}

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=1\textwidth]{../figs/stan-offset-panel-mean-resid-down.png}
\caption{The log-absolute value of downside (negative) residuals from the main
component model.
Figure looks qualitatively the same as Fig.~\ref{fig:resid} and so justifies
using variability (positive and negative residuals) as a measure of risk.}
\label{fig:resid-downside}
\end{center}
\end{figure}

% \begin{figure}[htbp]
% \begin{center}
% \includegraphics[width=0.9\textwidth]{../figs/lmer-vs-stan2.pdf}
% \caption{Comparison of }
% \label{fig:lmer-stan}
% \end{center}
% \end{figure}

>>>>

\documentclass[12pt]{article}
\usepackage{geometry}
\geometry{verbose, letterpaper, tmargin = 2.54cm, bmargin = 2.54cm,
  lmargin = 2.54cm, rmargin = 2.54cm}
\geometry{letterpaper}
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{setspace}
\usepackage{booktabs}
% \usepackage{verbatim}
\usepackage{amsmath}
\usepackage{url}
\usepackage{mathtools}
% \usepackage{lineno}
% \usepackage{xcolor}
% \renewcommand\linenumberfont{\normalfont\tiny\sffamily\color{gray}}
% \modulolinenumbers[2]

% % Linux Libertine:
% \usepackage{textcomp}
% \usepackage[sb]{libertine}
% \usepackage[varqu,varl]{inconsolata}% sans serif typewriter
% \usepackage[libertine,bigdelims,vvarbb]{newtxmath} % bb from STIX
% \usepackage[cal=boondoxo]{mathalfa} % mathcal
% %\useosf % osf for text, not math
% \usepackage[supstfm=libertinesups,%
%   supscaled=1.2,%
%   raised=-.13em]{superiors}

@@

% Fix line numbering and align environment
% http://phaseportrait.blogspot.ca/2007/08/lineno-and-amsmath-compatibility.html
% \newcommand*\patchAmsMathEnvironmentForLineno[1]{%
%   \expandafter\let\csname old#1\expandafter\endcsname\csname #1\endcsname
%   \expandafter\let\csname oldend#1\expandafter\endcsname\csname end#1\endcsname
%   \renewenvironment{#1}%
%      {\linenomath\csname old#1\endcsname}%
%      {\csname oldend#1\endcsname\endlinenomath}}%
% \newcommand*\patchBothAmsMathEnvironmentsForLineno[1]{%
%   \patchAmsMathEnvironmentForLineno{#1}%
%   \patchAmsMathEnvironmentForLineno{#1*}}%
% \AtBeginDocument{%
% \patchBothAmsMathEnvironmentsForLineno{equation}%
% \patchBothAmsMathEnvironmentsForLineno{align}%
% \patchBothAmsMathEnvironmentsForLineno{flalign}%
% \patchBothAmsMathEnvironmentsForLineno{alignat}%
% \patchBothAmsMathEnvironmentsForLineno{gather}%
% \patchBothAmsMathEnvironmentsForLineno{multline}%
% }

@@

We checked our models with a two-stage modelling approach
using the R package lme4 [49].
To do this, we fit the initial model of the mean component $\log(R_{i,t})$
and then fit the second model to the log absolute value of the
residuals, $\log | \widehat{\log(R_{i,t})} - \log(R_{i,t}) |$.
Most importantly, (1) this model does not carry uncertainty
from the first mean-component model to the variance-component model, but
(2) it also leaves the residuals in the mean-component model strongly
heteroskedastic and therefore improperly weights individual data points, and
(3) does not allow for proper modelling of the strategy-level predictors,
$\eta_1$ and $\eta_2$. Nonetheless, it provides a check that our results
from the Stan model are approximately correct and allowed us
to quickly iterate and build intuition about the models.
A version of the Stan model without the variance-component
matched the estimates of the same model in lme4 almost exactly.

@@

% \bibliographystyle{apalike}
% \bibliography{refs}

@@

\begin{table}[h!]
\scriptsize
  \centering
  \caption{Labels and descriptions of unique fishing strategies. In many cases,
a particular strategy represents a group of similar permits across areas
or vessel sizes. The column ``Main species'' indicates species that make up at
least 10\% of the total revenue across all years and individuals for that
fishing strategy. ``Sock'' refers to sockeye salmon.}
  \label{tab:strategies}
  \begin{tabular}{llll}
  \toprule
\input{strategy-table.tex}
  \end{tabular}
\end{table}

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=1\textwidth]{stan-gg-spoke-all.pdf}
\caption{The effect of adding a permit to one's strategy
on estimated revenue variability and median revenue.
This is an extended version of Fig.~2 that includes all major
strategy combinations.}
\label{fig:spoke-all}
\end{center}
\end{figure}

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=5in]{stan-main-effects.pdf}
\caption{Main effects from the hierarchical model
predicting revenue ($\beta$) and variability ($\gamma$) in revenue.
The $\eta$ coefficients represent strategy-level predictors
relating mean species diversity and mean days fished
within a strategy
(both centered by their means and divided by
two times their standard deivations)
to the magnitude of residual error.}
\label{fig:fe}
\end{center}
\end{figure}

@@

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=1.06\textwidth]{stan-str-posteriors-dot.pdf}
\caption{Estimates of within-strategy effects from the hierarchical model.
Panels refer to parameters in equations \ref{eq:mean} and \ref{eq:cv}.
Shown are medians (dots) and 50\% and 95\% credible intervals
(thick and thin line segments).
Strategies are ordered from high to low mean
species diversity from top to bottom.}
\label{fig:re}
\end{center}
\end{figure}

@@

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=1.05\textwidth]{stan-offset-break-anti-spaghetti.pdf}
\caption{Effects of (A) generalizing and (B) specializing from year-to-year for
  individual permit holders \emph{within} the \Sexpr{nstr} most common
  strategies. Changing species diversity from year-to-year is associated with
  higher variability for individuals within the strategies above the zero line.
  Generalizing (A) or specializing (B) is associated with greater expected
  revenue ratios to the right of the zero line and lower expected revenue ratios
  to the left of the zero line. These effects are estimated holding fishing
  season length constant from year-to-year. Dots and line segments represent
  medians and 50\% credible intervals of posteriors. Panel B and Fig.~4 are the
  same.}
\label{fig:mirror}
\end{center}
\end{figure}

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=0.6\textwidth]{stan-offset-break-anti-spaghetti-specializing-no-effort.pdf}
\caption{Same as Fig.~4 but without the effort (days fished) predictor and
  without its interaction with species diversity.}
\label{fig:noeffort}
\end{center}
\end{figure}

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=1\textwidth]{itq-combined.pdf}
\caption{The effect of IFQs (individual fishing quotas) on model estimates. (A)
  Posterior density of the ratio between strategy-level estimates of
  standardized revenue variability ($\gamma_{0j}$'s) after the introduction of
  IFQs vs.\ before the introduction of IFQs. (B) Estimates (medians) of the
  effect of generalizing (increasing species diversity) on variability
  ($\gamma_{1j}$'s) for the full model (``Grouped'') compared to a model where
  separate effects are estimated before and after IFQs were introduced (``IFQ
  split''). Pattern looks similar for the effect of specializing on variability
  ($\gamma_{2j}$'s) and is not shown.}
\label{fig:ifq}
\end{center}
\end{figure}

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=1\textwidth]{strategy-year-effects.pdf}
\caption{Strategy-year intercept estimates ($\beta_{0,j,t}$ in
Eq.~\ref{eq:mean}) from the hierarchical model.
Shown are 40 samples from the posterior distribution.}
\label{fig:str-yrs}
\end{center}
\end{figure}

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=1\textwidth]{stan-offset-panel-mean-resid.png}
\caption{The log-absolute value residuals from the mean-component model (Eq.~\ref{eq:mean}).
These residuals are modelled in the variance-component model
(Eq.~\ref{eq:cv}).
Breakpoint linear regression fits are overlaid in red for visual interpretation.}
\label{fig:resid}
\end{center}
\end{figure}

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=1\textwidth]{stan-offset-panel-mean-resid-down.png}
\caption{The log-absolute value of downside (negative) residuals from the main
component model.
Figure looks qualitatively the same as Fig.~\ref{fig:resid} and so justifies
using variability (positive and negative residuals) as a measure of risk.}
\label{fig:resid-downside}
\end{center}
\end{figure}

% \begin{figure}[htbp]
% \begin{center}
% \includegraphics[width=0.9\textwidth]{lmer-vs-stan2.pdf}
% \caption{Comparison of }
% \label{fig:lmer-stan}
% \end{center}
% \end{figure}
